О множествах точек на плоскости с целочисленными расстояниями

### 2019-09-20 AvdMomZvol_rails/Article.tex
From Zvolinsky
Final remarks

@@

TODO: rephrase?

TODO: can a scissors set have another axis of symmetry?

@@

TODO: pictures!

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.72\linewidth]{picture_8.png}}
\parbox{0.73\linewidth}{\caption{IPS of cardinality 15 and diameter 1888}
\label{picture_8.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.72\linewidth]{picture_9.png}}
\parbox{0.73\linewidth}{\caption{IPS of cardinality 16 and diameter 2189}
\label{picture_9.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.9\linewidth]{picture_13.png}}
\parbox{0.9\linewidth}{\caption{IPS of cardinality 17 and diameter 3224}
\label{picture_13.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.9\linewidth]{picture_14.png}}
\parbox{0.9\linewidth}{\caption{IPS of cardinality 18 and diameter 3696}
\label{picture_14.png}}
\end{figure}

@@

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.9\linewidth]{picture_17.png}}
\parbox{0.9\linewidth}{\caption{IPS of cardinality 21 and diameter 11692}
\label{picture_17.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.9\linewidth]{picture_18.png}}
\parbox{0.9\linewidth}{\caption{IPS of cardinality 22 and diameter 12296}
\label{picture_18.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.8\linewidth]{picture_19.png}}
\parbox{0.8\linewidth}{\caption{IPS of cardinality 23 and diameter 16027}
\label{picture_19.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.8\linewidth]{picture_20.png}}
\parbox{0.8\linewidth}{\caption{IPS of cardinality 24 and diameter 19758}
\label{picture_20.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.9\linewidth]{picture_21.png}}
\parbox{0.9\linewidth}{\caption{IPS of cardinality 25 and diameter 32054}
\label{picture_21.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.95\linewidth]{picture_22.png}}
\parbox{0.95\linewidth}{\caption{IPS of cardinality 26 and diameter 39516}
\label{picture_22.png}}
\end{figure}

@@

@@

\begin{figure}[htbp]
	\includegraphics[width=.48\linewidth]{picture_10.png}
	\hfill
	\includegraphics[width=.48\linewidth]{picture.png}
	\\
	\parbox{.48\linewidth}{\caption{PIPS of cardinality 8 and diameter 162}
	\label{picture_10.png}}
	\hfill
	\parbox{.48\linewidth}{\caption{PIPS of cardinality 8 and diameter 409}
	\label{picture.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.9\linewidth]{picture_11.pdf}}
\parbox{0.9\linewidth}{\caption{IPS of cardinality 12 and diameter 409}
\label{picture_11.pdf}}
\end{figure}

@@

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.9\linewidth]{picture_12.pdf}}
\parbox{0.9\linewidth}{\caption{IPS of cardinality 10 and diameter 56}
\label{picture_12.pdf}}
\end{figure}

@@

>>>>

Avdeev N.N., Zvolinsky R.E., Momot E.A.

On particular diameter bounds for integral point sets in higher dimensions

@@

%TODO: rephrase?

%TODO: can a scissors set have another axis of symmetry?

@@

%TODO: pictures!

@@

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.75\linewidth]{picture_8.png}}
\parbox{0.75\linewidth}{\caption{IPS of cardinality 15 and diameter 1888}
\label{picture_8.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.75\linewidth]{picture_9.png}}
\parbox{0.75\linewidth}{\caption{IPS of cardinality 16 and diameter 2189}
\label{picture_9.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.85\linewidth]{picture_13.png}}
\parbox{0.85\linewidth}{\caption{IPS of cardinality 17 and diameter 3224}
\label{picture_13.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.85\linewidth]{picture_14.png}}
\parbox{0.85\linewidth}{\caption{IPS of cardinality 18 and diameter 3696}
\label{picture_14.png}}
\end{figure}

@@

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.75\linewidth]{picture_17.png}}
\parbox{0.75\linewidth}{\caption{IPS of cardinality 21 and diameter 11692}
\label{picture_17.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.75\linewidth]{picture_18.png}}
\parbox{0.75\linewidth}{\caption{IPS of cardinality 22 and diameter 12296}
\label{picture_18.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.85\linewidth]{picture_19.png}}
\parbox{0.85\linewidth}{\caption{IPS of cardinality 23 and diameter 16027}
\label{picture_19.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.85\linewidth]{picture_20.png}}
\parbox{0.85\linewidth}{\caption{IPS of cardinality 24 and diameter 19758}
\label{picture_20.png}}
\end{figure}

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{picture_21.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 25 and diameter 32054}
\label{picture_21.png}}
\end{figure}

@@

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{picture_22.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 26 and diameter 39516}
\label{picture_22.png}}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=.48\linewidth]{picture_10.png}
	\hfill
	\includegraphics[width=.48\linewidth]{picture.png}
	\\
	\parbox{.48\linewidth}{\caption{PIPS of cardinality 8 and diameter 162}
	\label{picture_10.png}}
	\hfill
	\parbox{.48\linewidth}{\caption{PIPS of cardinality 8 and diameter 409}
	\label{picture.png}}
\end{figure}

@@

@@

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{picture_11.pdf}}
\parbox{1\linewidth}{\caption{IPS of cardinality 12 and diameter 409}
\label{picture_11.pdf}}
\end{figure}

@@

\section{Bounds based on pyramid sets}

@@

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{picture_12.pdf}}
\parbox{1\linewidth}{\caption{IPS of cardinality 10 and diameter 56}
\label{picture_12.pdf}}
\end{figure}

@@

\section{Final remarks}
All the given PIPSs were obtained through a combination of computer search an intuition of the authors;
so, the further search may lead to better bounds employing the same consructions.

There is still no general construction for a rails or scissors PIPS of given cardinality.
For rails PIPSs, we can conjecture that there exists a set of arbitrary cardinality with 2 points on one line
and all the rest on the other;
on the other hand, we still have not found any rails PIPSs with 4 and 5 points on the lines.

As for today, we have found pyramid PIPS of cardinality at most 9.

The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo
